%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.3 (30/3/2020)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-orange} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else


%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Nerushan}{Naguleswaran}
\address{111 - 80 Orenda Crt, Brampton, ON, Canada, L6W3M9}
\mobile{(647) 525-4544}

\email{nerushan.n@hotmail.com}
% \homepage{www.posquit0.com}
\github{Neru9898}
\linkedin{Nerushan Naguleswaran}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}

\position{Electrical Engineer{\enskip\cdotp\enskip}Striving Programmer{\enskip\cdotp\enskip}Enthusiastic Learner} % Your expertise/fields
% \quote{``Make the change that you want to see in the world."} % A quote or statement

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{\today}{\hspace{1cm}} % The company being applied to
\letterdate{\hspace{1cm}} % The date on the letter, default is the date of compilation

% \lettertitle{Job Application for Middle Manager} % The title of the letter

\letteropening{Dear Hiring Manager,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Resume} % Any enclosures with the letter

\makecvfooter{\today}{Nerushan Naguleswaran~~~·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header


\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}
%------------------------------------------------

\lettersection{About Me}

\tab I'm in my final year electrical engineering student at York University, expected to graduate with bachelor’s degree of engineering in June 2021. I have used many software during my studies and co-op like MATLAB, Simulink and Microsoft Office to analyze and organize data. As well, I've learned many programing languages such as C Java, Bash, Verilog, Unix/Linux Shell, Python and Node.js as seen on my resume. Aiming to learn more languages such as Javascript and React JS to become much more versatile in programing and very eager to further my skills. Furthermore, developed the ability working in different work environment either as a team or individual to accomplish task under multiple constraints. As well the ability to adapt to any situation that occurs in the period of accomplishing task and finding solutions to finish our goals in a timely manner.  

\tab My ability to work in groups was needed for my time at Toronto Hydro, where I was assigned to multiple projects working with many individuals. One project was called conversion project, where were given the task to convert meters to smart meter and update information in communication and customer software. This team mainly consisted of three students, technologist, and customer care specialist, where the students had to gather readings from the meter and initiate communication from both software. Using PL/SQL to gather the customer information and Excel to filter meters data, then after using MV90 to establish the new connection for the meter. Then finally, sending the green light to the customer specialist to finish up the process. I was responsible with diving work for my team and its completions. Using Excel helped to organize data within the students and later analyze the data received to send off to other members to the team. As well communicating among managing any issues during the process with my team and communicating among the team for possible solution. Then, updating out progress or concerns to our supervisor.

\tab I had to adapt to a new environment for my capstone project where there was an uncertainty of project scope and direction. Ultimately, the team chose to pursue a software project where we have to use new programing languages such as Python and Node.js, where I have acquired this skill by self teaching myself and in my spare time to attempt small project to build my skill. Using my knowledge to later apply to project. At the same time, learnt a new process of quality assurance and testing using a program called Postman, where it was to test the project platform. This helped finding errors in code and resolving them thought the implementation stages.

\tab I’m always eager to learn and explore new avenues to further my knowledge and skills. I have attached my resume with information of my work experiences and education. I hope to hear from you soon, reference can be provided upon request. Thank you for your time and consideration. 

% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.

%------------------------------------------------

% \lettersection{Why Initech?}

% Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.

%------------------------------------------------

% \lettersection{Why Me?}

% Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}